Redundant calibration as a complex optimization problem

### 2016-12-09 paper.tex
added some of the sparsity plots to the paper

\subsubsection{Spectral Condition Number}
kappa + itr plots
\begin{figure*}
\centering
\subfigure[$\kappa$]{\includegraphics[width=0.47\textwidth]{./kappa.pdf}\label{fig:kappa}}
% V_R_3.pdf: 585x441 pixel, 72dpi, 20.64x15.56 cm, bb=0 0 585 441
\subfigure[Iterations required before and after Preconditioning]{\includegraphics[width=0.47\textwidth]{./cg_itr.pdf}\label{fig:cg_itr}}
\caption{The graphs presented here were generated using the second experimental setup in Table~\ref{tab:ch_parm}. In the left panel we have plotted the spectral condition number $\kappa$ of the Hessian $\bH$, before (magenta and red curves) and after preconditioning (blue curve), at different SNR values as a function of the
number of antennas $N$ in the array. This plot shows us that we can drastically reduce the condition number of $\bH$ by preconditioning. Moreover, $\kappa$ is also
independent of the problem size (the number of antennas in the array). The fact that $\kappa$ is small and independent of problem size (effectively constant) implies that it simply drops out 
of Eq.~\eqref{eq:cg_bound}. The right hand panel confirms this result. In the right hand panel we have plotted the number of major iterations (line 6 of Algorithm \ref{algo:CG}) required by the conjugate 
gradient method to invert $\bH$, before (magenta and red curves) and after preconditioning (blue and green curves), at different SNR values as a function of the number of antennas $N$ in the array.  
The right hand panel therefore shows us that the number of major iterations needed by the preconditioned conjugate gradient method to invert $\bH$ is independent of the number of antennas in the array
and is much smaller than the dimension of $\bH$. 
\label{fig:sup_anti}} 
\end{figure*}

@@

As alluded to in section ..., the second factor that determines the computational complexity of the conjugate gradient method when used to perform redundant calibration is the amount of non-zero
entries in the Hessian matrix $\bH$, which is the matrix we are trying to invert. We have also shown in section that the first factor, the spectral condition number of $\bH$, can be reduced 
to a constant by employing preconditioning and can therefore be completely eliminated from the computational complexity equation. A useful matrix quantity
which we will use in this section is the sparsity factor $\gamma$ of a matrix, which is the ratio between the amount of zero entries and the total amount of entries in a matrix. We 
can therefore define $\gamma$ as follows:
\begin{equation}
 \gamma = \left (1 - \frac{m}{P^2} \right ) 
\end{equation}
It is trivial to determine an analytic expression for the sparsity ratio of $\bH$ when our redundant array is in a regular east-west geometric configuration
The sparsity and the asymptotic sparsity ratio of $\boldsymbol{H}$ are equal to
\begin{align}
\gamma &= \frac{5N^2-7N+3}{8N^2-8N+2} & \gamma_{\infty} &= \lim_{N\rightarrow \infty}\gamma = \frac{5}{8}. 
\end{align}
However when our redundant array makes use of a more complicated geometric layout it becomes much more difficult to construct such expressions as $\bH$ itself 
becomes much harder to express analytically.

@@

We can now use the sparsity factor to compute the order of the computational cost of inverting $\bH$ with
\begin{equation}
P^{c} = (1 - \gamma)P^2.
\end{equation}
Solving for $c$ we obtain
\begin{align}
c &= \log_{P}(1 - \gamma) + 2 & c_{\infty} &= \lim_{N\rightarrow \infty} c = 2.
\end{align}
Asymptotically the computational cost of inverting $\bH$ is $O(P^2)$. However, the computational cost converges 
very slowly to its asymptotic value, and in general is equal to $O(P^{c})$, where $c \sim 1.7$ if a Hexagonal geometric layout is employed.

@@

>>>>

\subsubsection{Spectral Condition Number}
kappa + itr plots
\begin{figure*}
\centering
\subfigure[$\kappa$]{\includegraphics[width=0.47\textwidth]{./kappa.pdf}\label{fig:kappa}}
% V_R_3.pdf: 585x441 pixel, 72dpi, 20.64x15.56 cm, bb=0 0 585 441
\subfigure[Iterations required before and after Preconditioning]{\includegraphics[width=0.47\textwidth]{./cg_itr.pdf}\label{fig:cg_itr}}
\caption{The graphs presented here were generated using the second experimental setup in Table~\ref{tab:ch_parm}. In the left panel we have plotted the spectral condition number $\kappa$ of the Hessian $\bH$, before (magenta and red curves) and after preconditioning (blue curve), at different SNR values as a function of the
number of antennas $N$ in the array. This plot shows us that we can drastically reduce the condition number of $\bH$ by preconditioning. Moreover, $\kappa$ is also
independent of the problem size (the number of antennas in the array). The fact that $\kappa$ is small and independent of problem size (effectively constant) implies that it simply drops out 
of Eq.~\eqref{eq:cg_bound}. The right hand panel confirms this result. In the right hand panel we have plotted the number of major iterations (line 6 of Algorithm \ref{algo:CG}) required by the conjugate 
gradient method to invert $\bH$, before (magenta and red curves) and after preconditioning (blue and green curves), at different SNR values as a function of the number of antennas $N$ in the array.  
The right hand panel therefore shows us that the number of major iterations needed by the preconditioned conjugate gradient method to invert $\bH$ is independent of the number of antennas in the array
and is much smaller than the dimension of $\bH$. 
\label{fig:kappa_itr}} 
\end{figure*}

@@

As alluded to in section ..., the second factor that determines the computational complexity of the conjugate gradient method when used to perform redundant calibration is the amount of non-zero
entries in the Hessian matrix $\bH$, which is the matrix we are trying to invert. We have also shown in section that the first factor, the spectral condition number of $\bH$, can be reduced 
to a constant by employing preconditioning and can therefore be completely eliminated from the computational complexity equation. A useful matrix quantity
which we will use in this section is the sparsity factor $\gamma$ of a matrix, which is the ratio between the amount of zero entries and the total amount of entries in a matrix. We 
can therefore define $\gamma$ as follows:
\begin{equation}
 \gamma = \left (1 - \frac{m}{P^2} \right ) 
\end{equation}
It is trivial to determine an analytic expression for the sparsity ratio of $\bH$ when our redundant array is in a regular east-west geometric configuration
The sparsity and the asymptotic sparsity ratio of $\boldsymbol{H}$ are equal to
\begin{align}
\gamma &= \frac{5N^2-7N+3}{8N^2-8N+2} & \gamma_{\infty} &= \lim_{N\rightarrow \infty}\gamma = \frac{5}{8} \label{eq:gamma}. 
\end{align}
However when our redundant array makes use of a more complicated geometric layout it becomes much more difficult to construct such expressions as $\bH$ itself 
becomes much harder to express analytically.

@@

We can now use the sparsity factor to compute the order of the computational cost of inverting $\bH$ with
\begin{equation}
P^{c} = (1 - \gamma)P^2.
\end{equation}
Solving for $c$ we obtain
\begin{align}
c &= \log_{P}(1 - \gamma) + 2 & c_{\infty} &= \lim_{N\rightarrow \infty} c = 2. \label{eq:c}
\end{align}
Asymptotically the computational cost of inverting $\bH$ is $O(P^2)$. However, the computational cost converges 
very slowly to its asymptotic value, and in general is equal to $O(P^{c})$, where $c \sim 1.7$ if a Hexagonal geometric layout is employed.

@@

\begin{figure*}
\centering
\subfigure[$\gamma$]{\includegraphics[width=0.47\textwidth]{./sparsity.pdf}\label{fig:kappa}}
% V_R_3.pdf: 585x441 pixel, 72dpi, 20.64x15.56 cm, bb=0 0 585 441
\subfigure[$c$]{\includegraphics[width=0.46\textwidth]{./comp_order.pdf}\label{fig:cg_itr}}
\caption{In the left panel we plot the sparsity ratio $\gamma$ (the number of zero entries relative to the total number of entries in a matrix) of the Hessian $\bH$ as a function of the number 
of antennas $N$ in the array for different geometries, namely an hexagonal grid (blue circles), a square grid (green crosses) and a regular east-west grid (red circles). For the regular east-west grid we are able to construct an analytical expression for $\gamma$ (the dashed red line). Taking the limit 
of this expression, Eq.~\eqref{eq:gamma}, as $N\rightarrow \infty$ produces the black dotted line. In the right panel we plot the order of the computational cost $c$ for inverting $\bH$ as a function of the number 
of antennas in the array for different geometries. We use the same color scheme in the right and left panels. We compute $c$ using Eq.~\eqref{eq:c}. We can again compute 
an analytic expression (dashed red line) for the east-west grid using Eq.~\eqref{eq:c} and Eq.~\eqref{eq:gamma}.  
\label{fig:sup_anti}} 
\end{figure*}
